Coupling finite and boundary element methods to solve the Poisson-Boltzmann equation for electrostatics in molecular solvation

### 2022-03-04 results.tex
Update of plots
I have added updated plots and removed the one that we are not using since they would create confusion on the repository.

\begin{figure}
\centering
\includegraphics[width=0.45\linewidth]{FEM_BEM_Arginine_varying_coeff_iter.png}
\includegraphics[width=0.45\linewidth]{FEM_BEM_Arginine_varying_coeff_time.png}
\includegraphics[width=0.45\linewidth]{Hybrid_FEM_BEM_Arginine_varying_coeff_iter.png}
\includegraphics[width=0.45\linewidth]{Hybrid_FEM_BEM_Arginine_varying_coeff_time.png}
\caption{Time-to-solution and iteration count to compute the solvation energy of arginine with a variable permittivity, using standard and hybrid FEM-BEM coupling. Can we make this only two plots?}
\label{fig:arg_variable}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_iter.png}
\includegraphics[width=0.45\linewidth]{Arginine_varying_coeff_time.png}
% \includegraphics[width=0.45\linewidth]{Hybrid_FEM_BEM_Arginine_varying_coeff_iter.png}
% \includegraphics[width=0.45\linewidth]{Hybrid_FEM_BEM_Arginine_varying_coeff_time.png}
\caption{Time-to-solution and iteration count to compute the solvation energy of arginine with a variable permittivity, using standard and hybrid FEM-BEM coupling. %Can we make this only two plots?
}
\label{fig:arg_variable}
\end{figure}
